\documentclass[12pt]{article}
\input{../MacroDefs/HeaderAssignment}
\usepackage{tfrupee}
\usepackage{fdsymbol}
 \begin{document}
 
\title{Assignment 2}%replace X with the appropriate number
\author{STAT 230\\
UAEU} %if necessary, replace with your course title
%\date{ $ 26^{th} $ August, 2019}
\date{}
 \maketitle\vspace{-.4in}
 \noindent
% \TextInBox{6 in }{Name: \vspace{.22 in}}\\
%\; \TextInBox{6.05 in }{ Enrolled As: \MCOption[1.2in]{PHD Student} \MCOption[1in]{RA}\MCOption[1 in]{TA}}\\
\TextInBox{6 in }{ 

  }\\
 \vspace{.4in}
 
 
 

%
%\DefBoxOne{}{
%\begin{center}\color{black}
%Part I:  Short answer type questions.
%\end{center}
%}


%\DefBoxOne{Notations}{
%$$ \Onebf_k=\left[ \begin{array}{c}1\\1\\\vdots \\1\end{array}\right]_{k\times 1} \text{ , }  J_{k}=\left[ \begin{array}{cccc}1&1 & \cdots & 1\\1& 1& \cdots&  1\\\vdots & \vdots & \ddots  &\vdots \\1& 1 &\cdots & 1\end{array}\right]_{k\times k} \text{ and } I_{k}=\left[ \begin{array}{cccc}1&0 & \cdots & 0\\0& 1& \cdots&  0\\\vdots & \vdots & \ddots  &\vdots \\0& 0 &\cdots & 1\end{array}\right]_{k\times k} \text{ for } k\in \Z_{+}.   $$
%
%}
\vspace{-.2in}
\DefBoxOne{}{
\begin{center}\color{black}
There are a total of 9 problems. You may review {\bf Unit3 slides} while answering the questions.   {\bf Show your steps to get entire credit for your solutions.   }
\end{center}
}


\begin{enumerate}




\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
Let $A$, $B$, $C$ be three events.  Use the basic  properties of probabilities to show that 
\begin{enumerate}
\item (2.5 points) $P(A\cup B  )\leq P(A)+P(B)$
\item(2.5 points)  $P(A\cup B \cup C  )\leq P(A)+P(B)+P(C)$
\item (2.5 points) $P(A\cap B )\geq P(A)+P(B)-1$
\item  (2.5 points) $P(A\cap B \cap C )\geq P(A)+P(B)+P(C)-2$
\end{enumerate}

}}{

}\\
\vspace{.1in}


\item \QuizQ{ \TextInBoxOne{5.4in}{
A car repair can be performed either on time or late and either satisfactorily or unsatisfactorily. The probability
of a repair being on time and satisfactory is 0.30. The
probability of a repair being on time is 0.75.  The
probability of a repair being satisfactory however it is performed late is 0.20. 

\begin{enumerate}
\item (8 points) What is the probability of a repair being late and unsatisfactory?
\item (7 points) What is the probability that the car repair is unsatisfactory?
\end{enumerate}

}}{

}\\

\vspace{.2in}

\item \QuizQ{ \TextInBoxOne{5.4in}{A student answers a multiple-choice examination question that offers four possible answers.
Suppose the probability that the student knows the answer to the question is .8 and the probability
that the student will guess is .2. Assume that if the student guesses, the probability of selecting the correct answer is .25. If the student correctly answers a question, what is the
probability that the student really knew the correct answer?
}}{

}\\

\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
(5 points) {\bf Two} A large group of people is to be checked for two common symptoms of a certain disease. It
is thought that 20\% of the people possess symptom A alone, 30\% possess symptom B alone,
10\%possess both symptoms, and the remainder have neither symptom. For one person chosen
at random from this group, find these probabilities:
\begin{enumerate}
\item The person has neither symptom.
\item The person has at least one symptom.
\item The person has both symptoms, given that he has symptom B.
\end{enumerate}
}}{

}\\
\vspace{.2in}



%\item \QuizQ{ \TextInBoxOne{5.4in}{
%In a popular  lottery game,  a person
%may pick any 5 numbers from $\{1, 2, \ldots ,52\} $ for her ticket.  How many different groups of 5 numbers can be chosen from the 52 {\bf if the repeated selection of the numbers is NOT allowed, however the ``order in which the numbers are selected are important" ?
%}}{
%}}
%
%
%\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
Medical case histories indicate that different illnesses may produce identical symptoms. Suppose that a particular set of symptoms, denoted H, occurs only when any one of three illnesses, $I_1$, $I_2$, or $I_3$, occurs.  Assume that the simultaneous occurrence ofmore that one of these illnesses is impossible and that $P(I_1) = .01, P(I_2) = .005, P(I_3) = .02.$ The probabilities of developing the set of symptoms H, given each of these illnesses, are known
to be $P( H \mid I_1) = .90, P( H \mid I_2) = .95, P( H \mid I_3) = .75.$
\begin{enumerate}
\item (5 points) Assuming that an ill person exhibits the symptoms, H, what is the probability that the person
has illness I1?
\end{enumerate}
}{
}}



\vspace{.2in}


\item \QuizQ{ \TextInBoxOne{5.4in}{Let A and B be any two events. Which of the following statements, in general, are false? 
\begin{enumerate}
\item (3 points) $P( A\mid B) + P( A\mid B) = 1$.
\item (4+3 points) $P( A\mid B) + P( A\mid B) = 1.?$ 
\item $P( A\mid B) + P( A\mid B) = 1.$
\end{enumerate} 
}{
}}


\vspace{.2in}






\item \QuizQ{ \TextInBoxOne{5.4in}{
(5 points ) A business tax form is either filed on time or late, is
either from a small or a large business, and is either
accurate or inaccurate. There is an 11\% probability that
a form is from a small business and is accurate and on
time. There is a 13\% probability that a form is from a
small business and is accurate but is late. There is a 15\%
probability that a form is from a small business and is on
time. There is a 21\% probability that a form is from a
small business and is inaccurate and is late.
\begin{enumerate}
\item If a form is from a small business and is accurate,
what is the probability that it was filed on time?
\item What is the probability that a form is from a large
business?
\end{enumerate}
}}{}

\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
(5 points ) 
A warning light in the cockpit of a plane is supposed to
indicate when a hydraulic pump is inoperative. If the
pump is inoperative, then there is a probability of 0.992
that the warning light will come on. However, there is a
probability of 0.003 that the warning light will come on
even when the pump is operating correctly. Furthermore,
there is a probability of 0.996 that the pump is operating
correctly. If the warning light comes on, what is the
probability that the pump really is inoperative?
}{

}}\\

%\vspace{.2in}
%\item \QuizQ{ \TextInBoxOne{5.4in}{
% Suppose that there is a practice session for a UAE football (soccer) team.   In that session all the 11 players randomly picked up a jersey from a basket where exactly 11 jerseys were kept.  Note that, all the jersey's have the players name written on it, therefore in the basket there were exactly one jersey that would match with a specific player.  
% \begin{enumerate}
% \item  (5 points )  What is the probability that {\bf  none} of the players have picked up the jersey that would match their name?
% \item  (5 points )  What is the probability that {\bf exactly three}  of the players have picked up the jersey that would match their name?
% \end{enumerate}
%}}{
%
%}\\


\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
 The marketing division of a company profiles its
potential customers and grades them as either likely or
unlikely purchasers. Overall, 16\% of the potential
customers are graded as likely purchasers. In reality,
81\% of the potential customers graded as likely
purchasers actually make a purchase, while only 9\% of
the potential customers graded as unlikely purchasers
actually make a purchase. If somebody made a purchase,
what is the probability that they had been graded as a
likely purchaser?
}}{

}\\



\vspace{.2in}


%
%\vspace{.2in}
%\item \QuizQ{ \TextInBoxOne{5.4in}{
%Given 20 people, what is the probability that,
%among the 12 months in the year, there are 4
%months containing exactly 2 birthdays and 4 containing
%exactly 3 birthdays?
%}{
%}}




%
%\item \QuizQ{ \TextInBoxOne{5.4in}{One of the sections in the class STAT230 has 10 students.  Assume the birthday of a student can be any one of days out of 365 days in a year.  We say that the two students share a (same) birthday if they are born on the same day and the same month {\small ( for example two students are born on $12^{\text{th}}$ January).}  Answer the following questions. 
%\begin{enumerate}
%\item How many different possibilities are there such that  exactly five students have the same birthday?
%\item How many different possibilities are there so that all the birthdays are on different days of the year. 
%\end{enumerate} 
%}{
%}}





\end{enumerate}






\end{document}