\documentclass[12pt]{article}
\input{../MacroDefs/HeaderAssignment}
\usepackage{tfrupee}
 \begin{document}
 
\title{Assignment 1}%replace X with the appropriate number
\author{STAT 230\\
UAEU} %if necessary, replace with your course title
%\date{ $ 26^{th} $ August, 2019}
\date{}
 \maketitle\vspace{-.4in}
 \noindent
% \TextInBox{6 in }{Name: \vspace{.22 in}}\\
%\; \TextInBox{6.05 in }{ Enrolled As: \MCOption[1.2in]{PHD Student} \MCOption[1in]{RA}\MCOption[1 in]{TA}}\\
\TextInBox{6 in }{ 

  }\\
 \vspace{.4in}
 
 
 

%
%\DefBoxOne{}{
%\begin{center}\color{black}
%Part I:  Short answer type questions.
%\end{center}
%}


%\DefBoxOne{Notations}{
%$$ \Onebf_k=\left[ \begin{array}{c}1\\1\\\vdots \\1\end{array}\right]_{k\times 1} \text{ , }  J_{k}=\left[ \begin{array}{cccc}1&1 & \cdots & 1\\1& 1& \cdots&  1\\\vdots & \vdots & \ddots  &\vdots \\1& 1 &\cdots & 1\end{array}\right]_{k\times k} \text{ and } I_{k}=\left[ \begin{array}{cccc}1&0 & \cdots & 0\\0& 1& \cdots&  0\\\vdots & \vdots & \ddots  &\vdots \\0& 0 &\cdots & 1\end{array}\right]_{k\times k} \text{ for } k\in \Z_{+}.   $$
%
%}
\DefBoxOne{}{
\begin{center}\color{black}
There are a total of 7 problems. You may review Unit1 and Unit2 slides while answering the questions.  Show your steps to get entire credit for your solutions. 
\end{center}
}


\begin{enumerate}





\item \QuizQ{ \TextInBoxOne{5.4in}{
 Let $\mathcal{S}= \{1,2,3,4,5,6\}$,
   $A=\{1,2,4, 6\}$,  $B=\{ 4,5 \}$,  and $C=\{5,6\}$.  Write down the explicit specification of the following sets
   \begin{enumerate}
   \item (4 points ) $A\cap B $
      \item  (2 points ) $A\cap B \cap C $
   \item (4 points ) $A\cup B \cup C$
\end{enumerate}    
Note that $\mathcal{S}$ denotes the universal set while $\emptyset$ is the notation for the Emptyset/Nullset. 
}}{

}\\

\vspace{.2in}


\item \QuizQ{ \TextInBoxOne{5.4in}{
Supose that A and B are two events. Write experssions involving unions, interactions and complements that describe the following:
\begin{enumerate}
\item (4 points ) Both events occur.
%\item  With or without air conditioning
\item  (3 points )  At least one occurs.
\item (3 points ) Neither occurs
\end{enumerate}
}}{

}\\

\vspace{.2in}


\item \QuizQ{ \TextInBoxOne{5.4in}{
(10 points ) A car manufacturer provides cars with the following different variations:
\begin{itemize}
\item Manual or automatic transmission
%\item  With or without air conditioning
\item  Two different stereo systems
\item Three possible exterior colors
\end{itemize}
How many different variations  of the car the manufacturer sells?
}}{

}\\

\vspace{.2in}

%\item \QuizQ{ \TextInBoxOne{5.4in}{
%In a popular  lottery game,  a person
%may pick any 5 numbers from $\{1, 2, \ldots ,52\} $ for her ticket.  How many different groups of 5 numbers can be chosen from the 52 {\bf if the repeated selection of the numbers is NOT allowed, however the ``order in which the numbers are selected are important" ?
%}}{
%}}
%
%
%\vspace{.2in}

\item \QuizQ{ \TextInBoxOne{5.4in}{
(10 points )  How many different `words' ({\small sequences of letters that may, or may not be a dictionary word }) can be constructed by permuting the letters of the word  \HLTY{\text{"ALMADAM"}}?
}{
}}


\vspace{.2in}

\item \QuizQ{ \TextInBoxOne{5.4in}{
Consider 8 tosses of a coin.  For example two typical sequences of outcomes that are considered different is  `HTHTTTTT', and `HHTTTTTT'.
\begin{enumerate}
\item (5 points )  What is the total number of different outcomes from the experiment?
\item (5 points )   How many different ways there can be exactly 3 heads?
\end{enumerate} 
}{
}}



\vspace{.2in}




\item \QuizQ{ \TextInBoxOne{5.4in}{
(10 points )  An investor has 30 thousand AED to invest among 3 possible investments.  Each investment must be in units of a thousand AED.  If the total 30 thousand AED is to be invested,  how many different investment strategies are possible?
}}{}

\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
If a dice is thrown 8 times and all the the 8 numbers (8-tuple) that appear are recorded.  Note that there is a total of $6^8= 1679616$  of  distinct possibilities for the ordered sequences of 8 numbers (distinct 8-tuples) that can occur.
\begin{enumerate}
\item (5 points )  In how many such 8-tuples, there is exactly three 6?
 \item (5 points )  In how many such 8-tuples, there is exactly three 6 and exactly two 1 ?
\end{enumerate}
}{
}}


%
%\item \QuizQ{ \TextInBoxOne{5.4in}{One of the sections in the class STAT230 has 10 students.  Assume the birthday of a student can be any one of days out of 365 days in a year.  We say that the two students share a (same) birthday if they are born on the same day and the same month {\small ( for example two students are born on $12^{\text{th}}$ January).}  Answer the following questions. 
%\begin{enumerate}
%\item How many different possibilities are there such that  exactly five students have the same birthday?
%\item How many different possibilities are there so that all the birthdays are on different days of the year. 
%\end{enumerate} 
%}{
%}}





\end{enumerate}






\end{document}