\documentclass[12pt]{article}
\input{../MacroDefs/HeaderAssignment}
\usepackage{tfrupee}
\usepackage{fdsymbol}
 \begin{document}
 
\title{Assignment 1}%replace X with the appropriate number
\author{STAT 230\\
UAEU} %if necessary, replace with your course title
%\date{ $ 26^{th} $ August, 2019}
\date{}
 \maketitle\vspace{-.4in}
 \noindent
% \TextInBox{6 in }{Name: \vspace{.22 in}}\\
%\; \TextInBox{6.05 in }{ Enrolled As: \MCOption[1.2in]{PHD Student} \MCOption[1in]{RA}\MCOption[1 in]{TA}}\\
\TextInBox{6 in }{ 

  }\\
 \vspace{.4in}
 
 
 

%
%\DefBoxOne{}{
%\begin{center}\color{black}
%Part I:  Short answer type questions.
%\end{center}
%}


%\DefBoxOne{Notations}{
%$$ \Onebf_k=\left[ \begin{array}{c}1\\1\\\vdots \\1\end{array}\right]_{k\times 1} \text{ , }  J_{k}=\left[ \begin{array}{cccc}1&1 & \cdots & 1\\1& 1& \cdots&  1\\\vdots & \vdots & \ddots  &\vdots \\1& 1 &\cdots & 1\end{array}\right]_{k\times k} \text{ and } I_{k}=\left[ \begin{array}{cccc}1&0 & \cdots & 0\\0& 1& \cdots&  0\\\vdots & \vdots & \ddots  &\vdots \\0& 0 &\cdots & 1\end{array}\right]_{k\times k} \text{ for } k\in \Z_{+}.   $$
%
%}
\DefBoxOne{}{
\begin{center}\color{black}
There are a total of 7 problems. You may review Unit1 and Unit2 slides while answering the questions.  Show your steps to get entire credit for your solutions. 
\end{center}
}


\begin{enumerate}





\item \QuizQ{ \TextInBoxOne{5.4in}{
 Suppose that there is a practice session for a UAE football (soccer) team.   In that session all the 11 players randomly picked up a jersey from a basket where exactly 11 jerseys were kept.  Note that, all the jerseys have the players name written on it, therefore in the basket there were exactly one jersey that would match with a specific player.  What is the probability that none of the players have picked up the jersey that would match their name?
}}{

}\\

\vspace{.2in}


\item \QuizQ{ \TextInBoxOne{5.4in}{
Three cards are selected randomly {\bf  without replacement} from the deck of 52 cards.
\begin{enumerate}
\item What is the probability that all the cards are  `Spades' ( $\spadesuit$)?
\item What is the probability that at least one of them is an `Ace'?
\end{enumerate}
}}{

}\\

\vspace{.2in}


\item \QuizQ{ \TextInBoxOne{5.4in}{
(10 points ) A car repair can be performed either on time or late and either satisfactorily or unsatisfactorily. The probability
of a repair being on time and satisfactory is 0.26. The
probability of a repair being on time is 0.74. The
probability of a repair being satisfactory is 0.41. What is
the probability of a repair being late and unsatisfactory?
}}{

}\\

\vspace{.2in}

%\item \QuizQ{ \TextInBoxOne{5.4in}{
%In a popular  lottery game,  a person
%may pick any 5 numbers from $\{1, 2, \ldots ,52\} $ for her ticket.  How many different groups of 5 numbers can be chosen from the 52 {\bf if the repeated selection of the numbers is NOT allowed, however the ``order in which the numbers are selected are important" ?
%}}{
%}}
%
%
%\vspace{.2in}

\item \QuizQ{ \TextInBoxOne{5.4in}{A typical ATM pin consists of 4 digits.  Assume that all the integers between $0$ to $9$ are equally likely for selecting each of the digits. Find the probability of the following events. 
\begin{enumerate}
\item What is the number of all possible different ATM passwords that a user can choose?
\item The bank has selected a group of 150 ATM users randomly.  What is the probability that atleast two of the users have exact same ATM pin? {\tiny \bf Assume that all the possible four digit numbers  are equally likely to be considered as a PIN of a randomly selected user. } Also, compute the probability upto 3 decimal places. 
\end{enumerate} 
}{
}}


\vspace{.2in}

\item \QuizQ{ \TextInBoxOne{5.4in}{
Consider 8 tosses of a coin.  For example two typical sequences of outcomes that are considered different is  `HTHTTTTT', and `HHTTTTTT'.
\begin{enumerate}
\item (5 points )  What is the total number of different outcomes from the experiment?
\item (5 points )   How many different ways there can be exactly 3 heads?
\end{enumerate} 
}{
}}



\vspace{.2in}




\item \QuizQ{ \TextInBoxOne{5.4in}{
(10 points )  An investor has 30 thousand AED to invest among 3 possible investments.  Each investment must be in units of a thousand AED.  If the total 30 thousand AED is to be invested,  how many different investment strategies are possible?
}}{}

\vspace{.2in}
\item \QuizQ{ \TextInBoxOne{5.4in}{
If a dice is thrown 8 times and all the the 8 numbers (8-tuple) that appear are recorded.  Note that there is a total of $6^8= 1679616$  of  distinct possibilities for the ordered sequences of 8 numbers (distinct 8-tuples) that can occur.
\begin{enumerate}
\item (5 points )  In how many such 8-tuples, there is exactly three 6?
 \item (5 points )  In how many such 8-tuples, there is exactly three 6 and exactly two 1 ?
\end{enumerate}
}{
}}


%
%\item \QuizQ{ \TextInBoxOne{5.4in}{One of the sections in the class STAT230 has 10 students.  Assume the birthday of a student can be any one of days out of 365 days in a year.  We say that the two students share a (same) birthday if they are born on the same day and the same month {\small ( for example two students are born on $12^{\text{th}}$ January).}  Answer the following questions. 
%\begin{enumerate}
%\item How many different possibilities are there such that  exactly five students have the same birthday?
%\item How many different possibilities are there so that all the birthdays are on different days of the year. 
%\end{enumerate} 
%}{
%}}





\end{enumerate}






\end{document}