\documentclass[12pt]{article}
\input{../MacroDefs/HeaderAssignment}
\usepackage{tfrupee}
\usepackage{fdsymbol}
\usepackage{latexcolors}
\usepackage{mathrsfs}
%\NewDocumentCommand{\support}{O{ }}{{\mathcal{S}}_{_{#1}}}
%\NewDocumentCommand{\support}{O{ }}{{\mathbb{S}}_{_{#1}}}
%\newcommand{\SampleS}{\mathcal{S}}
\newcommand{\SampleS}{\mathscr{S}}
\newcommand{\Not}[1]{\overline{#1}}
\newcommand{\Center}[1]{{\begin{center}#1 \vspace{-.2in}
\end{center}}}
\newcommand{\Exmpl}[2]{\qBrd[0.75in]{#1}{Example #2:}}
\newcommand{\pmf}{p}
\newcommand{\binP}{\pi}

 \begin{document}
 
\title{}%replace X with the appropriate number
\author{} %if necessary, replace with your course title
%\date{ $ 26^{th} $ August, 2019}
\date{}
% \maketitle\vspace{-.in}
 \noindent
% \TextInBox{6 in }{Name: \vspace{.22 in}}\\
%\; \TextInBox{6.05 in }{ Enrolled As: \MCOption[1.2in]{PHD Student} \MCOption[1in]{RA}\MCOption[1 in]{TA}}\\
\TextInBox{6 in }{ 

  }\\
 \vspace{.4in}
 
 
 

%
%\DefBoxOne{}{
%\begin{center}\color{black}
%Part I:  Short answer type questions.
%\end{center}
%}


%\DefBoxOne{Notations}{
%$$ \Onebf_k=\left[ \begin{array}{c}1\\1\\\vdots \\1\end{array}\right]_{k\times 1} \text{ , }  J_{k}=\left[ \begin{array}{cccc}1&1 & \cdots & 1\\1& 1& \cdots&  1\\\vdots & \vdots & \ddots  &\vdots \\1& 1 &\cdots & 1\end{array}\right]_{k\times k} \text{ and } I_{k}=\left[ \begin{array}{cccc}1&0 & \cdots & 0\\0& 1& \cdots&  0\\\vdots & \vdots & \ddots  &\vdots \\0& 0 &\cdots & 1\end{array}\right]_{k\times k} \text{ for } k\in \Z_{+}.   $$
%
%}


\vspace{-.2in}
\DefBoxOne{}{
\begin{center}\color{black}
\Large A Few Problems Aiming the Midterm Exam
\end{center}
}


\vspace{.2in}

\begin{enumerate}
\qbx[6.3in]{teal!40}{\item   An airline has four flights (4 flight numbers) from New-York to California and five flights  (5 different flight numbers ) from California to
Hawaii per day.  If the flights are to be made on separate days, how many different flight
arrangements can the airline offer from New-York to Hawaii?}\\

\vspace{2in}


\qbx[6.4in]{amethyst!40}{
\item A car manufacturer provides cars with the following different variations:
\begin{itemize}
\item Manual or automatic transmission
%\item  With or without air conditioning
\item  Three different stereo systems
\item Four possible exterior colors
\end{itemize}
How many different types of car the manufacturer sells?
}\\
\vspace{2in}







\qbx[6.4in]{babyblue!60}{ \item  How many different numbers can be constructed using a 64 bits binary digits? 
} \\
\vspace{2in}







\qbx[6.4in]{cherryblossompink!50}{
\item A typical lisence plate number in Abu-Dhabi consists of 5 digits.  How many different lisence plate numbers (excluding `00000') are possible that esnds with 2 ? 
}\\


\vspace{2in}

%\qbx[6.4in]{bluebell!40}{\item 
%How many different batting orders are possible for a cricket team consisting of 11 players?}\\

\qbx[6.4in]{cambridgeblue!50}{\Exmpl{cambridgeblue}{}
How many different ``words" ({\tiny sequence of three letters that may or may not be dictionary words}) can you make with the letters
\HLTW{\text{"MISSISSIPPI"}}?}\\
\vspace{2in}




\qbx[6.4in]{carnationpink!50}{\item 
A class in probability theory consists of \HLTW{ \text{10 men}} and \HLTW{\text{ 8 women}}.  An examination is given, and the students are ranked
according to their performance. Assume that no two students
obtain the same score.
\begin{enumerate}
\item[a).] How many different rankings are possible?
\item[b).]  Assuming equally likeli setup, what is the probability a Female student appears to be first rank.  
\end{enumerate}}\\

\vspace{2in}



\qbx[6.4in]{apricot!40}{\item 
An investor has 20 thousand dollars to invest among 4 possible investments.  Each investment must be in units of a thousand dollars. If the total 20 thousand is to be invested, 
\begin{enumerate}
\item how many different investment strategies are possible?
\item  how many different investment strategies are possible  if not all the money need be invested?
\end{enumerate}    
}\\
\vspace{2in}



\qbx[6.4in]{teal!40}{\item 
 12  identical balls are distributed among 4 kids. Assuming all possible of number of distributions of the balls are equally likely, idensity the following probabilities.  What is probability that each of the  kids obtains one ball or more?
}\\
\vspace{2in}




\qbx[6.4in]{bronze!40}{
\item A smoke detector system uses two devices, A and B. If smoke is present, the probability that
it will be detected by device \HLTY{A} is \HLTW{0.95}; by device \HLTY{B},\HLTW{0.90}; and assume that both the devices work independently. 
\begin{enumerate}
\item If smoke is present, find the probability that the smoke will be \HLTW{\text{detected by either device A or B, or both devices.}}
\item Find the probability that the smoke will be undetected.
\end{enumerate}
 }\\
\vspace{2in}





\qbx[6.4in]{bronze!40}{
\item A smoke detector system uses two devices, A and B. If smoke is present, the probability that
it will be detected by device \HLTY{A} is \HLTW{0.95}; by device \HLTY{B},\HLTW{0.90}; and by both devices, \HLTW{0.88}.
\begin{enumerate}
\item If smoke is present, find the probability that the smoke will be \HLTW{\text{detected by either device A or B, or both devices.}}
\item Find the probability that the smoke will be undetected.
\end{enumerate}
 }\\
 \vspace{3.5in}
 
 
 
 
 
 \qbx[6.4in]{babyblue!40}{
\Exmpl{babyblue!50}{} Suppose that A and B are mutually exclusive events for which \HLTW{P(A) =0 .3} and \HLTW{P(B) = 0.5}. What is the probability that 
\begin{enumerate}
\item either A or B occurs?
\item A occurs but B does not?
\item both A and B occur?
\end{enumerate}
 }\\
 \vspace{3in}
 
 
 \qbx[6.4in]{airforceblue!40}{
\item  A car repair can be performed either on time or late and either satisfactorily or unsatisfactorily. The probability
of a repair being on time and satisfactory is 0.26. The
probability of a repair being on time is 0.74. The
probability of a repair being satisfactory is 0.41. What is
the probability of a repair being late and unsatisfactory?
 }\\
 \vspace{4in}
 
 
 
 \qbx[6.4in]{olive!40}{
Let $A, B$ be two events such that  $$P(A) = \frac{2}{3} \text{ and } P(\Not{B}) = \frac{1}{4}.$$Can A and B be disjoint? Explain.}\\
 
 \vspace{3in}
 
 

\qbx[6.4in]{purple!30}{\item  A fair-dice is thrown 8 times and all the the 8 numbers  that appear are recorded.  
\begin{enumerate}
\qBrd[4in]{applegreen!40}{ \item What is the probability that there is  no $\HLTW{Six}$?}
\qBrd[4in]{babyblue!40}{ \item What is the probability that there is at least one $\HLTW{Six}$?}
\qBrd[4in]{amber!40}{ \item What is the probability that there will  be exactly 3 $\HLTW{Four}$'s and 2 $\HLTW{Three}$'s among the eight throws?}
\end{enumerate}
\vspace{.05in}
} \\
\vspace{4in}

\qbx[6.4in]{amber(sae/ece)!40}{\item
A typical ATM pin consists of 4 digits.  Assume that all the integers between $0$ to $9$ are equally likely for selecting each of the digits. Find the probability of the following events. 
\begin{enumerate}
\item What is the probability that all the four digits of a randomly selected ATM pin is different?
\item *The bank has selected a group of 120 ATM users randomly.  What is the probability that atleast two of the users have exact same ATM pin? {\tiny Assume that all the possible four digit numbers  are equally likely to be considered as a PIN of a randomly selected user. }
\item *What would be corresponding probability if 175 ATM users are  randomly chosen instead?
\end{enumerate}  }\\
\vspace{3in}


\qbx[6.4in]{capri!40}{
\item   A card is selected randomly from the deck of 52 cards.
\begin{itemize}
\item Let $A$ be the event that the card is an `Ace'.
\item  Let $B$ be the event that the card is either  `King' or a 'Queen'.
\item  Let $C$ be the event that the card is  `Diamonds'.
\end{itemize}
 \begin{enumerate}
 \item Is the events $A$ and $B$ statistically independent? (Justify your answer)
  \item Is the events $B$ and $c$ statistically independent? (Justify your answer)
 \end{enumerate}
}\\
\vspace{3in}
 
 \qbx[6.4 in]{teal!30}{\item  If two events, A and B, are such that $P( A)=0.6$, $P(B)=0.2$, and $P( A\cap B)= 0.1$, find the following
\begin{enumerate}
\item $P(A\mid B)$
\item $P(B\mid A)$
\item $P(A\mid A\cup B)$
\end{enumerate}
 }\\
 \vspace{2in}
 
 
 \qbx[6.4in]{applegreen!30}{\item  An insurance company believes that people can be divided into two classes: those who are accident prone and those who are not. 
The companys statistics show that an accident-prone person will have an accident at some time within a fixed 1-year period with probability $0.4$, whereas this probability is $0.2$ for a person who is not accident prone.  If we assume that $30\%$
 of the population is accident prone, what is the probability
that a new policyholder will have an accident within a year of
purchasing a policy?
}\\
 \vspace{2.5in}
 
 
 
\qbx[6.4in]{amethyst!40}{
An insurance company believes that people can be divided into two classes: those who are accident prone and those who are not. 
The companys statistics show that an accident-prone person will have an accident at some time within a fixed 1-year period with probability $0.4$, whereas this probability is $0.2$ for a person who is not accident prone.  If we assume that $30\%$
 of the population is accident prone. \\
 Suppose that a new policyholder has an accident within a year of purchasing a policy. What is the probability that he or she is accident prone?
}\\ \vspace{2.5in}

\qbx[6.4in]{babyblue!40}{
\item   Suppose that we toss 2 fair dice. Let $E_1$ denote the
event that the sum of the dice is 6 and F denote the event that the
first die equals 4.  Is $E_1$ statistically independent of $F$?\\
}\\ \vspace{2.5in}

\qbx[6.4in]{teal!40}{ \item  If two events $A$, and $B$ are statistically independent, then 
\begin{enumerate}
\item  $A$ and $\Not{B}$ are also statistically independent, 
\item  $\Not{A}$ and ${B}$ are also statistically independent. 
\item  $\Not{A}$ and $\Not{B}$ are also statistically independent. 
\end{enumerate}
}\\ \vspace{2.5in}

\qbx[6.4 in]{amethyst!40}{
\item   If A and B are independent events with \HLTW{P( A) = 0.5} and \HLTW{P( B) = 0.2}, find the following:
\begin{enumerate}
\qBrd[.75in]{applegreen!30}{\item $P(A\cap B)$}\hspace{.1in}
\qBrd[.75in]{amber!30}{\item $P(A\cup B)$}\hspace{.1in}
\qBrd[.75in]{applegreen!30}{\item $P(\Not{A}\cap \Not{B})$}\hspace{.1in}
\qBrd[.75in]{amber!30}{\item $P(\Not{A}\cup \Not{B})$}\hspace{.1in}
\end{enumerate}
}\\

 \vspace{2.5in}
\qbx[6.4 in]{amber!40}{\item 
A diagnostic test for a disease is such that it (correctly) detects the disease in 92\% of the individuals who actually have the disease. Also, if a person does not have the disease, the test will report that he or she does not have it with probability 0.9. Only 2\%  of the population has the
disease in question. If a person is chosen at random from the population and the diagnostic test
indicates that she has the disease, what is the conditional probability that she does, in fact, have
the disease? Are you surprised by the answer? Would you call this diagnostic test reliable?}\\
 \vspace{3.5in}
 
 
 \qbx[6.4in]{airforceblue!30}{\item
After production, an electrical circuit is given a quality
score of A, B, C, or D. Over a certain period of time,
$77\%$ of the circuits were given a quality score A,
$11\%$ were given a quality score B, $7\%$ were given a
quality score C, and $5\%$ were given a quality score D.
Furthermore, it was found that $2\%$ of the circuits given a
quality score A eventually failed, and the failure rate was
$10\%$ for circuits given a quality score B, $14\%$ for circuits
given a quality score C, and $25\%$ for circuits given a
quality score D.
\begin{enumerate}
\item If a circuit did not fail, what is the probability that it
had received a quality score A?
\item If a circuit failed, what is the probability that it had
received a quality score either C or D?
\end{enumerate}
}\\
 \vspace{2.5in}

\qbx[6.4 in]{antiquefuchsia!40}{\item    We know the following about a colormetric method used to test lake water for nitrates. If
water specimens contain nitrates, a solution dropped into the water will cause the specimen to
turn red 95\% of the time. When used on water specimens without nitrates, the solution causes
the water to turn red 10\% of the time (because chemicals other than nitrates are sometimes
present and they also react to the agent). Past experience in a lab indicates that nitrates are
contained in 30\%of the water specimens that are sent to the lab for testing. If a water specimen is randomly selected
\begin{enumerate}
\item from among those sent to the lab, what is the probability that it will turn red when tested?
\item It it turns red when tested, what is the probability that it actually contains nitrates?
\end{enumerate}
}\\ \vspace{3in}

\qbx[6.4in]{teal!40}{
\item  Four radar sets, operating independently, are set to detect any aircraft flying through a certain area.  Each set has a probability of $.95$ to correctly detect a plane in its area. If an aircraft enters the area, what is the probability that it
\begin{enumerate}
\item goes undetected?
\item is detected by at least one  radar set?
\item is detected by exactly 2 radars?
\item is detected by at least  2 radars?
\end{enumerate}
}\\
 \vspace{3in}
 
 
 
 
\qbx[6.4in]{brightube!40}{\item 
Consider 6 tosses of a fair coin.  {\tiny For example, two typical sequences of outcomes that are considered different is  $\HLTW{`HTTTTT'}$, and $\HLTW{`THTTTT'}$.}
\begin{enumerate}
\item What is the probability that there are be exactly 2 Heads ?
\item What is the probability that there are be exactly 4 Heads ?
\item What is the probability that there are no Heads?
\item What is the probability that there is at least one Tail?
\end{enumerate} 
}\\
 \vspace{4in}
 
 
\qbx[6.4in]{amethyst!40}{
\item  If $A$ and $B$ are two  events such that $P(A)>0$ and $P(B>0)$ then, 
\begin{enumerate}
\item If the events A and B are Statistically Independent then they can not be disjoint./mutually exclushive. 
\item If the events A and B are disjoint then they can not be statistically independent. 
\end{enumerate}
   }  \\
    \vspace{3in}
   
   \qBrd[6.4in]{airforceblue!30}{
\item 
Suppose a random variable $X$ has the following support $\support[X]= \{1, 2,3, 4, 5\}$. 
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\hline\hline
x    & 1    & 2    & 3 & 4& 5    \\ \hline\hline
$\pmf_{_X}(x)$ &$ \frac{1}{5}$ & $ \frac{2}{5}$  &$ \frac{1}{10}$  & \HLTY{ c} &$ \frac{1}{10}$   \\ \hline\hline
\end{tabular}
\end{center}
\begin{enumerate}
\item What is the value of \HLTY{ c} so that $\pmf_{_X}(x)$ become a valid probability mass function on the support $\support[X]$?
\item What is the probability that $X\in A$, where the event $A=\{2, 4\}$.
\item  What is the expected value of the random variable?
\end{enumerate}
}\\
 \vspace{3in}

\qbx[6.4in]{amethyst!50}{
\item  If X be a discrete random variable on the support $\support[X]=\{1, 2, 3, 4\}$ with the corresponding  pmf specified as  
$\pmf_{_X}(1)= \frac{1}{4}, \pmf_{_X}(2)= \frac{1}{2}, \pmf_{_X}(3)= \frac{1}{8}$, and $\pmf_{_X}(4)= \frac{1}{8}$. Calculate the Expected value  of $X$. 
}\\
 \vspace{2.5in}

\qbx[6.4in]{olive!50}{\item 
The probability distribution of $X$, the number of daily network blackouts is given by
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline\hline
$x\in \support[X]$    & 0    & 10    & 40    \\ \hline
$\pmf_{_X}(x)$ & 0.7 & 0.2 & 0.1 \\ \hline\hline
\end{tabular}
\end{center}
\begin{enumerate}
\item Find the Expected value,  variance of the random variable {\bf X}.
\item Find the MGF of the random variable {\bf X}.
\item Find  $\HLTW{E\left( \frac{1}{2+|{X}|} \right) }$
\item Find  $\HLTW{E\left( \sqrt{X+1} \right) }$
\item Find the CDF of the distribution.
\end{enumerate}
}\\

 \vspace{2.5in}
 
 
 
\qbx[6.4in]{ceil!40}{\item 
Derive the MGF of the Poisson$(\lambda)$ distribution where $\lambda>0$. 
}\\
 \vspace{2in}

%\qbx[6.4in]{ceil!40}{\item 
%Derive Mean of a  Poisson$(\lambda)$ distribution where $\lambda>0$. 
%}\\

%\qbx[6.4in]{ceil!40}{\item 
%Derive the Mean/Expected Value   of a Binomial$(n, \binP)$ distribution where $1>\binP>0$, and $n\in \mathbb{Z}_{+}$.  
%}\\


%\qbx[6.4in]{ceil!40}{\item 
%Derive the Mean/Expected Value   of a Geometric$(\binP)$ distribution where $1>\binP>0$.  
%}\\

\qbx[6.4in]{ceil!40}{\item 
Derive the MGF of a Geometric$(\binP)$ distribution where $1>\binP>0$.  
}\\
 \vspace{2in}

\qbx[6.4in]{ceil!40}{\item 
Derive the MGF of a Poisson$(\lambda)$ distribution where $\lambda>0$.  
}\\
 \vspace{2in}

\qBrd[4.5in]{babyblue!30}{
\item 
If $X\sim \text{Binomial}(n=50, \binP=0.1)$ then
\begin{enumerate}
\item Obtain the value of $E(X)$, $\text{Var}(X)$, and $ E(X^2) $.
\item What is the MGF of X?
\end{enumerate} 
}\\
 \vspace{2in}
 
\qBrd[4.5in]{babyblue!30}{
\item 
If $X\sim \text{Geometric}(\binP=0.2)$ then
\begin{enumerate}
\item Obtain the value of $E(X)$, $\text{Var}(X)$, and $ E(X^2) $.
\item What is $E(4X+10)$?
\item  What is Var$(4X+10)$?
\item What is the MGF of X?
\end{enumerate} 
}\\
 \vspace{4in}

\qBrd[4.5in]{babyblue!30}{
\item 
If $X\sim \text{Poisson}(\lambda=5)$,  then
\begin{enumerate}
\item Obtain the value of $E(X)$, $\text{Var}(X)$, and $ E(X^2)$
\item What is $E(3X+50)$?
\item What is Var$(3X+50)$?
\item What is the MGF of X?
\end{enumerate} 
}\\
 \vspace{3in}

\qbx[6.4in]{apricot!50}{
\item 
Of a population of consumers, 60\% are reputed to prefer a particular brand, A, of toothpaste. If a group of randomly selected consumers is interviewed, 
\begin{enumerate}
\item what is the probability that {\bf exactly 3 }  people have to be interviewed to encounter the first consumer who prefers brand A?
\item  what is the probability that {\bf at least }  3 people have to be interviewed to encounter the first consumer who prefers brand A?
\end{enumerate}	
}\\

 \vspace{3.5in}
%\qbx[6.4in]{apricot!50}{
%\item \vspace{.1in}
%\qBrd[4.5in]{amethyst!30}{ $M_{X}(t)= \frac{0.9e^t}{ 1 - 0.1 e^t}$,  What is the distribution of $X$? }\\
%\vspace{.1in}
%\qBrd[4.5in]{amethyst!30}{ $M_{X}(t)= \exp{\left(7e^t-7\right)}$,  What is the distribution of $X$? }\\
%\vspace{.1in}
%\qBrd[4.5in]{amethyst!30}{ $M_{X}(t)= \frac{1}{8}(1 + e^t)^3$,  What is the distribution of $X$? }\\
%\vspace{.1in}
%\qBrd[4.5in]{amethyst!30}{ $M_{X}(t)= \frac{1}{8}(1 + e^t)^3$,  What is the distribution of $X$? }\\
%\vspace{.1in}
%\qBrd[4.5in]{amethyst!30}{ $M_{X}(t)= \frac{8e^t}{ 10 - 2 e^t}$,  What is the distribution of $X$? }\\
%}\\

\qbx[6.4in]{airforceblue!30}{
\item 
Customers arrive at a checkout counter in a department store according to a Poisson distribution at an average of seven per hour. 
\begin{enumerate}
\item During a given hour, what are the probabilities that no more than two customers arrive?
\item During a given hour, what are the probabilities that exactly five customers arrive?
\item During a {\bf given two hours period}, what are the probabilities that exactly 6 customers arrive?
\end{enumerate}
}\\
 \vspace{3.5in}
%
%\qbx[6.4in]{teal!30}{
%\item 
%Suppose that a lot of  electrical fuses contains 5\% defectives. If a sample of 8 fuses is tested,  
%\begin{enumerate}
%\item find the probability of observing exactly  one defective.
%\item  find the probability of observing at least one defective.
%\item What is the expected number of defective fuses?
%\end{enumerate}
%}\\


\qbx[6.4in]{amber!30}{
\item 
On a specific project, an oil exploration firm has decided to allocate the required  finance  for 10 explorations. The probability of a particular exploration being successful is 0.10  .  Assume the explorations are statisticallly independent to each other.
\begin{enumerate}
\item Find the mean and variance of the number of successful explorations.
\item Suppose the firm has a fixed cost of \$20,000 in preparing equipment prior to doing its first exploration. If each successful exploration costs \$30,000 and each unsuccessful
exploration costs \$15,000, find the expected total cost to the firm for its ten explorations.
\end{enumerate}
}\\
 \vspace{3.5in}

\qbx[6.4in]{amber!30}{
\item 
An oil prospector will drill a succession of holes in a given area to find a productive well. The probability that he is successful on a given trial is 0.1.
\begin{enumerate}
\item What is the probability that the third hole drilled is the first to yield a productive well?
\item What is the expected number of drills that are required to get the first productive well?
\end{enumerate}
}\\
 \vspace{3in}

\qbx[6.4in]{amber!30}{
\item 
An oil prospector will drill a succession of holes in a given area to find a productive well. The probability that he is successful on a given trial is 0.40.  The company wants to fund  as much drills that are required to obtain 3 productive wells. 
\begin{enumerate}
\item What is the probability that the company need 9 drills to obtain the 3 productive wells. 
\item What is the expected number of drills that are required to get the first productive well?
\item Suppose the firm require a fixed cost of \$20,000 in preparing equipment prior to doing its first exploration.  If each successful exploration costs \$0,000 and each unsuccessful
exploration costs \$10,000.  Compute the expected budget that is required to be allocated for the project.
\end{enumerate}
}\\
 \vspace{3in}

%\qbx[6.4in]{amber!30}{
%\item 
%On a specific project, an oil exploration firm has decided to allocate the required  finance  for 10 explorations. The probability of a particular exploration being successful is 0.10  .  Assume the explorations are statisticallly independent to each other.
%\begin{enumerate}
%\item Find the mean and variance of the number of successful explorations.
%\item Suppose the firm has a fixed cost of \$20,000 in preparing equipment prior to doing its first exploration. If each successful exploration costs \$30,000 and each unsuccessful
%exploration costs \$15,000, find the expected total cost to the firm for its ten explorations.
%\end{enumerate}
%}\\


\qbx[6.4in]{asparagus!30}{
\item  An airline company have sold 50 tickets of a specific route of flight.  From the past experiences,  the company knows that the probability of a randomly selected customer would cancel ticket is    $2\%$.  Assume that the customers (if cancels ) cancels tickets independently.
\begin{enumerate}
\item what is the probability that exactly two customers will cancel their ticket.
\item What is the expected number of coustomers who may cancel their tickets.  
\end{enumerate}
}\\
 \vspace{3in}

\qbx[6.4in]{babyblue!30}{
\item A particular sale involves four items randomly selected from a large lot that is known to contain 10\% defectives.  Let Y denote the number of defectives among the 20 sold. The purchaser of the items will return the defectives for repair, and the repair cost is given by $\HLTW{U = 3Y^2 + Y + 2}$.  Find the expected repair cost, $E(U)$.
}\\
 \vspace{3in}
\end{enumerate}
\end{document}