\documentclass[12pt]{article}
\input{../MacroDefs/HeaderAssignment}
\usepackage{tfrupee}
\usepackage{fdsymbol}
\usepackage{latexcolors}
\usepackage{mathrsfs}
%\NewDocumentCommand{\support}{O{ }}{{\mathcal{S}}_{_{#1}}}
%\NewDocumentCommand{\support}{O{ }}{{\mathbb{S}}_{_{#1}}}
%\newcommand{\SampleS}{\mathcal{S}}
\newcommand{\SampleS}{\mathscr{S}}
\newcommand{\Not}[1]{\overline{#1}}
\newcommand{\Center}[1]{{\begin{center}#1 \vspace{-.2in}
\end{center}}}
\newcommand{\Exmpl}[2]{\qBrd[0.75in]{#1}{Example #2:}}
\newcommand{\pmf}{p}
\newcommand{\binP}{\pi}

 \begin{document}
 
\title{}%replace X with the appropriate number
\author{} %if necessary, replace with your course title
%\date{ $ 26^{th} $ August, 2019}
\date{}
% \maketitle\vspace{-.in}
 \noindent
% \TextInBox{6 in }{Name: \vspace{.22 in}}\\
%\; \TextInBox{6.05 in }{ Enrolled As: \MCOption[1.2in]{PHD Student} \MCOption[1in]{RA}\MCOption[1 in]{TA}}\\
\TextInBox{6 in }{ 

  }\\
 \vspace{.4in}
 
 
 

%
%\DefBoxOne{}{
%\begin{center}\color{black}
%Part I:  Short answer type questions.
%\end{center}
%}


%\DefBoxOne{Notations}{
%$$ \Onebf_k=\left[ \begin{array}{c}1\\1\\\vdots \\1\end{array}\right]_{k\times 1} \text{ , }  J_{k}=\left[ \begin{array}{cccc}1&1 & \cdots & 1\\1& 1& \cdots&  1\\\vdots & \vdots & \ddots  &\vdots \\1& 1 &\cdots & 1\end{array}\right]_{k\times k} \text{ and } I_{k}=\left[ \begin{array}{cccc}1&0 & \cdots & 0\\0& 1& \cdots&  0\\\vdots & \vdots & \ddots  &\vdots \\0& 0 &\cdots & 1\end{array}\right]_{k\times k} \text{ for } k\in \Z_{+}.   $$
%
%}


\vspace{-.2in}
\DefBoxOne{}{
\begin{center}\color{black}
\Large A Few Problems Aiming the Midterm Exam
\end{center}
}


\vspace{.2in}

\begin{enumerate}
\qbx[6.3in]{teal!40}{\item   An airline has four flights (4 flight numbers) from New-York to California and five flights  (5 different flight numbers ) from California to
Hawaii per day.  If the flights are to be made on separate days, how many different flight
arrangements can the airline offer from New-York to Hawaii?}\\

\qbx[6.4in]{amethyst!40}{
\item A car manufacturer provides cars with the following different variations:
\begin{itemize}
\item Manual or automatic transmission
%\item  With or without air conditioning
\item  Three different stereo systems
\item Four possible exterior colors
\end{itemize}
How many different types of car the manufacturer sells?
}\\


\qbx[6.4in]{babyblue!60}{ \item  How many different numbers can be constructed using a 64 bits binary digits? 
} \\

\qbx[6.4in]{cherryblossompink!50}{
\item A typical lisence plate number in Abu-Dhabi consists of 5 digits.  How many different lisence plate numbers (excluding `00000') are possible that esnds with 2 ? 
}\\




\qbx[6.4in]{bluebell!40}{\item 
How many different batting orders are possible for a cricket team consisting of 11 players?}\\

\qbx[6.4in]{cambridgeblue!50}{\Exmpl{cambridgeblue}{}
How many different ``words" ({\tiny sequence of three letters that may or may not be dictionary words}) can you make with the letters
\HLTW{\text{"MISSISSIPPI"}}?}\\

\qbx[6.4in]{carnationpink!50}{\item 
A class in probability theory consists of \HLTW{ \text{10 men}} and \HLTW{\text{ 8 women}}.  An examination is given, and the students are ranked
according to their performance. Assume that no two students
obtain the same score.
\begin{enumerate}
\item[a).] How many different rankings are possible?
\item[b).]  Assuming equally likeli setup, what is the probability a Female student appears to be first rank.  
\end{enumerate}}\\



\qbx[6.4in]{apricot!40}{\item 
An investor has 20 thousand dollars to invest among 4 possible investments.  Each investment must be in units of a thousand dollars. If the total 20 thousand is to be invested, 
\begin{enumerate}
\item how many different investment strategies are possible?
\item  how many different investment strategies are possible  if not all the money need be invested?
\end{enumerate}    
}\\

\qbx[6.4in]{teal!40}{\item 
 12  identical balls are distributed among 4 kids. Assuming all possible of number of distributions of the balls are equally likely, idensity the following probabilities.  What is probability that each of the  kids obtains one ball or more?
}\\

\qbx[6.4in]{bronze!40}{
\item A smoke detector system uses two devices, A and B. If smoke is present, the probability that
it will be detected by device \HLTY{A} is \HLTW{0.95}; by device \HLTY{B},\HLTW{0.90}; and assume that both the devices work independently. 
\begin{enumerate}
\item If smoke is present, find the probability that the smoke will be \HLTW{\text{detected by either device A or B, or both devices.}}
\item Find the probability that the smoke will be undetected.
\end{enumerate}
 }\\


\qbx[6.4in]{bronze!40}{
\item A smoke detector system uses two devices, A and B. If smoke is present, the probability that
it will be detected by device \HLTY{A} is \HLTW{0.95}; by device \HLTY{B},\HLTW{0.90}; and by both devices, \HLTW{0.88}.
\begin{enumerate}
\item If smoke is present, find the probability that the smoke will be \HLTW{\text{detected by either device A or B, or both devices.}}
\item Find the probability that the smoke will be undetected.
\end{enumerate}
 }\\
 
 
 \qbx[6.4in]{babyblue!40}{
\Exmpl{babyblue!50}{} Suppose that A and B are mutually exclusive events for which \HLTW{P(A) =0 .3} and \HLTW{P(B) = 0.5}. What is the probability that 
\begin{enumerate}
\item either A or B occurs?
\item A occurs but B does not?
\item both A and B occur?
\end{enumerate}
 }\\
 
 
 \qbx[6.4in]{airforceblue!40}{
\item  A car repair can be performed either on time or late and either satisfactorily or unsatisfactorily. The probability
of a repair being on time and satisfactory is 0.26. The
probability of a repair being on time is 0.74. The
probability of a repair being satisfactory is 0.41. What is
the probability of a repair being late and unsatisfactory?
 }\\
 
 \qbx[6.4in]{olive!40}{
Let $A, B$ be two events such that  $$P(A) = \frac{2}{3} \text{ and } P(\Not{B}) = \frac{1}{4}.$$Can A and B be disjoint? Explain.}\\
 
 \qbx[6.4in]{brightube!40}{\item 
Consider 6 tosses of a fair coin.  {\tiny For example, two typical sequences of outcomes that are considered different is  $\HLTW{`HTTTTT'}$, and $\HLTW{`THTTTT'}$.}
\begin{enumerate}
\item What is the probability that there are be exactly 2 Heads ?
\item What is the probability that there are be exactly 4 Heads ?
\item What is the probability that there are no Heads?
\item What is the probability that there is at least one Tail?
\end{enumerate} 
}\\


\qbx[6.4in]{purple!30}{\item  A fair-dice is thrown 8 times and all the the 8 numbers  that appear are recorded.  
\begin{enumerate}
\qBrd[4in]{applegreen!40}{ \item What is the probability that there is  no $\HLTW{Six}$?}
\qBrd[4in]{babyblue!40}{ \item What is the probability that there is at least one $\HLTW{Six}$?}
\qBrd[4in]{amber!40}{ \item What is the probability that there will  be exactly 3 $\HLTW{Four}$'s and 2 $\HLTW{Three}$'s among the eight throws?}
\end{enumerate}
\vspace{.05in}
} \\


\qbx[6.4in]{amber(sae/ece)!40}{\item
A typical ATM pin consists of 4 digits.  Assume that all the integers between $0$ to $9$ are equally likely for selecting each of the digits. Find the probability of the following events. 
\begin{enumerate}
\item What is the probability that all the four digits of a randomly selected ATM pin is different?
\item *The bank has selected a group of 120 ATM users randomly.  What is the probability that atleast two of the users have exact same ATM pin? {\tiny Assume that all the possible four digit numbers  are equally likely to be considered as a PIN of a randomly selected user. }
\item *What would be corresponding probability if 175 ATM users are  randomly chosen instead?
\end{enumerate}  }\\



\qbx[6.4in]{capri!40}{
\item   A card is selected randomly from the deck of 52 cards.
\begin{itemize}
\item Let $A$ be the event that the card is an `Ace'.
\item  Let $B$ be the event that the card is either  `King' or a 'Queen'.
\item  Let $C$ be the event that the card is  `Diamonds'.
\end{itemize}
 \begin{enumerate}
 \item Is the events $A$ and $B$ statistically independent? (Justify your answer)
  \item Is the events $B$ and $c$ statistically independent? (Justify your answer)
 \end{enumerate}
}\\
 
 \qbx[6.4 in]{teal!30}{\item  If two events, A and B, are such that $P( A)=0.6$, $P(B)=0.2$, and $P( A\cap B)= 0.1$, find the following
\begin{enumerate}
\item $P(A\mid B)$
\item $P(B\mid A)$
\item $P(A\mid A\cup B)$
\end{enumerate}
 }\\
 
 \qbx[6.4in]{applegreen!30}{\item  An insurance company believes that people can be divided into two classes: those who are accident prone and those who are not. 
The companys statistics show that an accident-prone person will have an accident at some time within a fixed 1-year period with probability $0.4$, whereas this probability is $0.2$ for a person who is not accident prone.  If we assume that $30\%$
 of the population is accident prone, what is the probability
that a new policyholder will have an accident within a year of
purchasing a policy?
}\\

\qbx[6.4in]{amethyst!40}{
An insurance company believes that people can be divided into two classes: those who are accident prone and those who are not. 
The companys statistics show that an accident-prone person will have an accident at some time within a fixed 1-year period with probability $0.4$, whereas this probability is $0.2$ for a person who is not accident prone.  If we assume that $30\%$
 of the population is accident prone. \\
 Suppose that a new policyholder has an accident within a year of purchasing a policy. What is the probability that he or she is accident prone?
}\\

\qbx[6.4in]{babyblue!40}{
\item   Suppose that we toss 2 fair dice. Let $E_1$ denote the
event that the sum of the dice is 6 and F denote the event that the
first die equals 4.  Is $E_1$ statistically independent of $F$?\\
}\\

\qbx[6.4in]{teal!40}{ \item  If two events $A$, and $B$ are statistically independent, then 
\begin{enumerate}
\item  $A$ and $\Not{B}$ are also statistically independent, 
\item  $\Not{A}$ and ${B}$ are also statistically independent. 
\item  $\Not{A}$ and $\Not{B}$ are also statistically independent. 
\end{enumerate}
}\\

\qbx[6.4 in]{amethyst!40}{
\item   If A and B are independent events with \HLTW{P( A) = 0.5} and \HLTW{P( B) = 0.2}, find the following:
\begin{enumerate}
\qBrd[.75in]{applegreen!30}{\item $P(A\cap B)$}\hspace{.1in}
\qBrd[.75in]{amber!30}{\item $P(A\cup B)$}\hspace{.1in}
\qBrd[.75in]{applegreen!30}{\item $P(\Not{A}\cap \Not{B})$}\hspace{.1in}
\qBrd[.75in]{amber!30}{\item $P(\Not{A}\cup \Not{B})$}\hspace{.1in}
\end{enumerate}
}\\


\qbx[6.4 in]{amber!40}{\item 
A diagnostic test for a disease is such that it (correctly) detects the disease in 92\% of the individuals who actually have the disease. Also, if a person does not have the disease, the test will report that he or she does not have it with probability 0.9. Only 2\%  of the population has the
disease in question. If a person is chosen at random from the population and the diagnostic test
indicates that she has the disease, what is the conditional probability that she does, in fact, have
the disease? Are you surprised by the answer? Would you call this diagnostic test reliable?}\\

 \qbx[6.4in]{airforceblue!30}{\item
After production, an electrical circuit is given a quality
score of A, B, C, or D. Over a certain period of time,
$77\%$ of the circuits were given a quality score A,
$11\%$ were given a quality score B, $7\%$ were given a
quality score C, and $5\%$ were given a quality score D.
Furthermore, it was found that $2\%$ of the circuits given a
quality score A eventually failed, and the failure rate was
$10\%$ for circuits given a quality score B, $14\%$ for circuits
given a quality score C, and $25\%$ for circuits given a
quality score D.
\begin{enumerate}
\item If a circuit did not fail, what is the probability that it
had received a quality score A?
\item If a circuit failed, what is the probability that it had
received a quality score either C or D?
\end{enumerate}
}\\

\qbx[6.4 in]{antiquefuchsia!40}{\item    We know the following about a colormetric method used to test lake water for nitrates. If
water specimens contain nitrates, a solution dropped into the water will cause the specimen to
turn red 95\% of the time. When used on water specimens without nitrates, the solution causes
the water to turn red 10\% of the time (because chemicals other than nitrates are sometimes
present and they also react to the agent). Past experience in a lab indicates that nitrates are
contained in 30\%of the water specimens that are sent to the lab for testing. If a water specimen is randomly selected
\begin{enumerate}
\item from among those sent to the lab, what is the probability that it will turn red when tested?
\item It it turns red when tested, what is the probability that it actually contains nitrates?
\end{enumerate}
}\\

\qbx[6.4in]{teal!40}{
\item  Four radar sets, operating independently, are set to detect any aircraft flying through a certain area.  Each set has a probability of $.95$ to correctly detect a plane in its area. If an aircraft enters the area, what is the probability that it
\begin{enumerate}
\item goes undetected?
\item is detected by at least one  radar set?
\item is detected by exactly 2 radars?
\item is detected by at least  2 radars?
\end{enumerate}
}\\


\qbx[6.4in]{amethyst!40}{
\item  If $A$ and $B$ are two  events such that $P(A)>0$ and $P(B>0)$ then, 
\begin{enumerate}
\item If the events A and B are Statistically Independent then they can not be disjoint./mutually exclushive. 
\item If the events A and B are disjoint then they can not be statistically independent. 
\end{enumerate}
   }  \\
   
   
   \qBrd[6.4in]{airforceblue!30}{
\item 
Suppose a random variable $X$ has the following support $\support[X]= \{1, 2,3, 4, 5\}$. 
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|}
\hline\hline
x    & 1    & 2    & 3 & 4& 5    \\ \hline\hline
$\pmf_{_X}(x)$ &$ \frac{1}{5}$ & $ \frac{2}{5}$  &$ \frac{1}{10}$  & \HLTY{ c} &$ \frac{1}{10}$   \\ \hline\hline
\end{tabular}
\end{center}
\begin{enumerate}
\item What is the value of \HLTY{ c} so that $\pmf_{_X}(x)$ become a valid probability mass function on the support $\support[X]$?
\item What is the probability that $X\in A$, where the event $A=\{2, 4\}$.
\end{enumerate}
}\\


\qbx[6.4in]{amethyst!50}{
\item  If X be a discrete random variable on the support $\support[X]=\{1, 2, 3, 4\}$ with the corresponding  pmf specified as  
$\pmf_{_X}(1)= \frac{1}{4}, \pmf_{_X}(2)= \frac{1}{2}, \pmf_{_X}(3)= \frac{1}{8}$, and $\pmf_{_X}(4)= \frac{1}{8}$. Calculate the CDF function of $X$. 
}\\

\qbx[6.4in]{olive!50}{\item 
The probability distribution of $X$, the number of daily network blackouts is given by
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline\hline
x    & 0    & 1    & 2    \\ \hline
$\pmf_{_X}(x)$ & 0.7 & 0.2 & 0.1 \\ \hline\hline
\end{tabular}
\end{center}
Find the Expected value,  variance, and MGF of the random variable {\bf X}.
}\\
\end{enumerate}



\end{document}